Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-01-29 awipev-CO2.Rmd
extract data for K. Wolf and minor editing

@@

@@

## pHs 
Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of 2273 µmoles.kg-1 (mean data). 
For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.

@@

```{r Klara Wolf}

>>>>

The instrument is usually calibrated against CRM standards after deployment, CRMs are run after 3 months as samples (measurement mode, not calibration mode), an then immediately calibrated again. This procedure is repeated every 3 months.

@@

####**Calibration**

- 2019-01-29 14:10: calibration started by Philipp Fisher using CRM XXX (XXXXX umol/kg). The three previous measurements were X1, X2, X3 and the three subsequent measurements were Y1, Y2, Y3.

@@

## pHs 
Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of 2273 µmoles kg-1 (mean data). For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.

@@

<!-- ```{r Klara Wolf} -->
<!-- wolf <- d_all %>% -->
<!--   dplyr::select(datetime, PCO2_Corr_filtered, phcalc, pH_calc_norm4) %>% -->
<!--   dplyr::filter(datetime >= "2016-03-01" & datetime <= "2016-09-30") -->
<!-- write_csv(path = "wolf.csv", wolf, col_names = TRUE) -->
<!-- ``` -->
